Topic Scores

### 2019-02-19 Topic Scores.Rmd
course content recommendations based on key words

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
beta_descriptions <- LDA_model %>%
  get_beta

gamma_descriptions <- LDA_model %>%
  get_gamma
```

## simulating students and key words
```{r student simulation}
terms <- unique(beta_descriptions$term)

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_descriptions%>%
  filter(term %in% student$kw_climate) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

@@

student$course_score <- gamma_descriptions     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )

View(student$course_score)
```
###Other comparison functions
```{r other functions}
#
##Binary
product <- function(a = gamma, b = B_score){
  X = a*b
}

>>>>

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
# k=10, 20, 35
beta_description <- lapply(
  LDA_model,
  get_beta
)

gamma_descriptions <- lapply(
  LDA_model,
  get_gamma
)

```
##Inspect topics
```{r inspect topics}
topics <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(10, beta)

#
##View
View(topics)

```
## simulating students and key words
```{r student simulation}
terms <- unique(beta_description$k35$term)

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_description$k35%>%
  filter(term %in% student$kw_policy) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

@@

student$course_score <- gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
```
###View
```{r View course}
View(student$topic_score)
View(student$course_score)
```
###Other comparison functions
```{r other functions}
#
##Binary
product <- function(a = gamma, b = B_score){
  X = a*b
}
